---
title: "JPG1400 Assignment 3 - Logistic Regression"
author: "your name here"
output: html_notebook
---

```{r include = FALSE}
library(httr)
```

```{r}
# create a data folder
dir.create("./data")

# use the GET command from httr to download a file and write it to disk
GET(url = "https://dl.dropboxusercontent.com/s/9hn8mjbrnbat63a/michelin_in_ny.csv?dl=0", 
    write_disk("./data/michelin_in_ny.csv", overwrite = TRUE))

michelin <- read.csv("./data/michelin_in_ny.csv")
```

In this lab you will conduct a logistic regression on the dataset ”MichelinNY.csv” in the lab folder. This dataset contains data on restaurants inclusion/exclusion based on a number of predictors, like food quality, décor, service level, and price.

Your job will be to use these various indicators of the restaurants to understand how they predict the probability of being a Michelin Star Restaurant (or not).

You will submit to me your “final” model after you’ve performed descriptive statistics, an analysis of deviance and pearson residuals, a ROC curve, leverage, and other diagnostics discussed in class.

You must show evidence to me that these diagnostic techniques were used in the creation of your final model. Like last time, I don’t need to see every test and diagnostic plot performed at every stage and iteration in your modeling process, but you should be able to tell me the story of how you arrived at your final model using examples of what you learned from the diagnostics along the way. So a few representative concrete examples will help. Also, I would like to see evidence that your final model is valid, again accounting for fit and validity.

Your report should also contain a section on interpreting the final model specification. This should contain a written formula for the regression line, and the written interpretation of the effect of each variable on the probability of being a Michelin Star Restaurant. Do the odds make sense? Why or why not?

From a time perspective, I imagine this assignment will take 3-5 hours to complete. Good luck!